---
title: "A Simulation of Marriage Data compared to Real Marriage Data in Toronto"
subtitle: ""
author: 
  - Richard Guo
thanks: "Code and data are available at: https://github.com/Richard-Guo1/Marriage_Liscence_Stats.git."
date: today
date-format: long
abstract: "The Covid-19 Pandemeic caused economic slowdowns in multiple sectors in Toronto. This paper aims to discover if the Marriage industry was one of the affected sectors. A Null-hypothesis of no change in the number of marriages was modeled with a random poisson distribution with Lambda of 10. It can be rejected if the data taken from Open Data Toronto looks significantly different."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

```


# Introduction

You can and should cross-reference sections and sub-sections. We use @talia, @opendatatoronto, and @rohan.

The remainder of this paper is structured as follows. @sec-mydatasection



# Data {#sec-mydatasection}

Below is a graph reflecting the number of marriages per month from 2011 to 2025 across all sectors of Toronto (@fig-marriage), from @opendatatoronto.

```{r}
#| label: fig-marriage
#| fig-cap: Number of Marriages per Month in Toronto
#| echo: false

data |> 
  ggplot(aes(x = date, y = marriage_licenses)) +
  geom_point()

```

From the years 2011 through 2020, we can observe similar trends and the amount of marriages month over month and year over year. During 2020 and the following years, a significant decrease in the amount of marriage licences is also observable. A simple conjecture is that the decrease was caused by the lock-downs in response to the Covid-19 pandemic. A sudden spike in the number of marriages c. March 2022 aligns with when many social distancing restrictions were loosened in Toronto.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)





# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional data details



\newpage


# References


